Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-07-20 manuscripts/manuscript1.qmd
added outcomes data

```{r setup}
#     axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = rel(0.5), margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(1)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_blank(),
      panel.background = element_blank(),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@

bob <- ich_aggressive |>
  tabyl(neurosurgery_evac, ich_laterality) |>
  adorn_percentages("col") |>
  adorn_pct_formatting(digits = 1) |>
  adorn_ns(position = "front") |>
  filter(neurosurgery_evac == "Yes")

ich_aggressive |>
  tabyl(days_mechanical_ventilation, ich_laterality)

>>>>

```{r setup}
#| echo: false
#| output: false

#| echo: false
#| fig-height: 12

library(targets)
library(tidyverse)
library(withr)
library(here)
library(formattable)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(flextable)

# plot stuff
theme_ich <- function(base_family = "Figtree",
                      base_size = 10) {
  theme_minimal(base_size = base_size) +
    theme(
      text = element_text(lineheight = 2),
      plot.title = element_text(size = rel(1.3), margin = margin(12, 0, 8, 0)),
      plot.subtitle = element_text(size = rel(1.1), margin = margin(4, 0, 0, 0)),
      axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = 12, margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(2)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_line(colour = "#F3F4F5"),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@
